Combining global tree cover loss data with historical national forest cover maps to look at six decades of deforestation and forest fragmentation in Madagascar

### 2018-03-19 manuscript/manuscript.Rnw
Link to Cirad Dataverse

{\small
  \begin{flushleft}  
    $[1]$ \textbf{Joint Research Center of the European Commission} -- Bio-economy Unit, I-21027 Ispra (VA), ITALY\\
    $[2]$ \textbf{Cirad} -- UPR Forêts et Sociétés, F-34398 Montpellier, FRANCE\\
    $[3]$ \textbf{ETC Terra}, F-75020 Paris, FRANCE\\
    $[4]$ \textbf{Office National pour l'Environnement}, 101 Antananarivo, MADAGASCAR\\
    $[5]$ \textbf{Wildlife Conservation Society}, 101 Antananarivo, MADAGASCAR\\
    $[6]$ \textbf{GreenInfo Network}, Oakland, California, USA\\
    ~\\
    $[\star]$ \textbf{Corresponding author:}
    \textbackslash{E-mail}:~ghislain.vieilledent@cirad.fr
    \textbackslash{Phone}:~+39.033.278.3516\\
  \end{flushleft}}

@@

Finally for all forest cover maps from 1973, isolated single
non-forest pixels (i.e.~fully surrounded by forest pixels) were
recategorized as forest pixels.  Doing so, forest cover increased from
about 95,000~ha for year 1953 to about 600,000~ha for year 2010. This
allowed us to avoid counting very small scale events (\textless 0.1
ha, such as selective logging or wind-throw) as deforestation. It also
prevents us from underestimating forest cover and overestimating
forest fragmentation. All the resulting maps have been made
permanently and freely available on the Zenodo research data
repository at \url{https://doi.org/10.5281/zenodo.1145785}.

@@

The authors thank two anonymous reviewers for useful comments on a
previous version of the manuscript. They also thank Peter Vogt for
useful advice on which metric to use to estimate forest
fragmentation. This study is part of the Cirad's BioSceneMada project
(\url{https://bioscenemada.cirad.fr}) and the Joint Research Center's
ReCaREDD project (\url{http://forobs.jrc.ec.europa.eu/recaredd}). The
BioSceneMada project is funded by FRB (Fondation pour la Recherche sur
la Biodiversité) and the FFEM (Fond Français pour l'Environnement
Mondial) under the project agreement AAP-SCEN-2013~I. The ReCaREDD
project is funded by the European Commission. The authors declare that
there are no conflicts of interest related to this article.

@@

All the data and the script used for this study have been made permanently and publicly available
on the Zenodo research data repository so that the results are entirely reproducible:
\begin{itemize}
\item Input data: \url{https://doi.org/10.5281/zenodo.1118955}
\item Script: \url{https://doi.org/10.5281/zenodo.1118484}
\item Output data: \url{https://doi.org/10.5281/zenodo.1145785}
\end{itemize}

>>>>

{\small
  \begin{flushleft}  
    $[1]$ \textbf{Joint Research Center of the European Commission} -- Bio-economy Unit, I-21027 Ispra (VA), ITALY\\
    $[2]$ \textbf{CIRAD} -- UPR Forêts et Sociétés, F-34398 Montpellier, FRANCE\\
    $[3]$ \textbf{ETC Terra}, F-75020 Paris, FRANCE\\
    $[4]$ \textbf{Office National pour l'Environnement}, 101 Antananarivo, MADAGASCAR\\
    $[5]$ \textbf{Wildlife Conservation Society}, 101 Antananarivo, MADAGASCAR\\
    $[6]$ \textbf{GreenInfo Network}, Oakland, California, USA\\
    ~\\
    $[\star]$ \textbf{Corresponding author:}
    \textbackslash{E-mail}:~ghislain.vieilledent@cirad.fr
    \textbackslash{Phone}:~+39.033.278.3516\\
  \end{flushleft}}

@@

Finally for all forest cover maps from 1973, isolated single
non-forest pixels (i.e.~fully surrounded by forest pixels) were
recategorized as forest pixels. Doing so, forest cover increased from
about 95,000~ha for year 1953 to about 600,000~ha for year 2010. This
allowed us to avoid counting very small scale events (\textless 0.1
ha, such as selective logging or wind-throw) as deforestation. It also
prevents us from underestimating forest cover and overestimating
forest fragmentation.

@@

The authors thank two anonymous reviewers for useful comments on a
previous version of the manuscript. They also thank Peter Vogt for
useful advice on which metric to use to estimate forest
fragmentation. This study is part of the CIRAD's BioSceneMada project
(\url{https://bioscenemada.cirad.fr}) and the Joint Research Center's
ReCaREDD project (\url{http://forobs.jrc.ec.europa.eu/recaredd}). The
BioSceneMada project is funded by FRB (Fondation pour la Recherche sur
la Biodiversité) and the FFEM (Fond Français pour l'Environnement
Mondial) under the project agreement AAP-SCEN-2013~I. The ReCaREDD
project is funded by the European Commission. The authors declare that
there are no conflicts of interest related to this article.

@@

Data and code used for this study have been made permanently and publicly available
on the CIRAD Dataverse repository so that the results are entirely reproducible:
\begin{itemize}
\item Input data: \url{http://dx.doi.org/10.18167/DVN1/2FP7LR}
\item Code: \url{http://dx.doi.org/10.18167/DVN1/275TDF}
\item Output data: \url{http://dx.doi.org/10.18167/DVN1/AUBRRC}
\end{itemize}
